### 2021-10-12 text/outline/outline.tex
update intro

Despite their extraordinary promise, single-cell CRISPR screens present substantial statistical challenges. A major difficulty is that CRISPR perturbations are (i) unobserved and (ii) assigned randomly to cells. These facts together imply that the analyst cannot know with certainty which cells were perturbed in a single-cell CRISPR screen experiment. The analyst instead must leverage an indirect, noisy proxy of perturbation presence or absence -- namely, transcribed barcode counts -- to ``guess'' which cells were perturbed. Using these imputed perturbation assignments, the analyst can attempt to estimate the effect of the perturbation on gene expression. The standard approach, which we call the ``thresholding method,'' is to assign perturbation identities to cells by thresholding the barcode counts.

We study estimation and inference in single-cell CRISPR screen experiments  from a statistical perspective, casting the data generating mechanism as a new class of errors-in-variables (or measurement error) models. We assume that the response variable $y$ is a GLM of an underlying predictor variable $x^*$. We do not observe $x^*$ directly; rather, we observe a noisy version $x$ of $x^*$ that itself is a GLM of $x^*$. The goal of the analysis is to estimate (and perform inference on) the effect of $x^*$ on $y$ using the observed data $(x, y)$. In the context of the biological application, $x^*$, $y$, and $x$ are perturbations, gene expressions, and barcode counts, respectively.

% First, within the proposed GLM-EIV

	% \item In summary we couple a novel statistical method -- GLM-EIV -- to powerful technologies from genomics and computer science -- CRISPR genome engineering, single-cell sequencing, clound computing, and high-performance computing -- to yield new statistical and biological insights.
% \end{itemize}

@@

>>>>

Despite their promise, single-cell CRISPR screens present substantial statistical challenges. A major difficulty is that CRISPR perturbations are (i) unobserved and (ii) assigned randomly to cells. The analyst cannot know with certainty which cells were perturbed and instead must leverage an indirect, noisy proxy of perturbation presence or absence -- namely, transcribed barcode counts -- to ``guess'' which cells were perturbed. Using these imputed perturbation assignments, the analyst can attempt to estimate the effect of the perturbation on gene expression. The standard approach, which we call the ``thresholding method,'' is to assign perturbation identities to cells by thresholding the barcode counts.

We study estimation and inference in single-cell CRISPR screens from a statistical perspective, formulating the data generating mechanism as a new class of errors-in-variables (or measurement error) models. We assume that the response variable $y$ is a GLM of an underlying predictor variable $x^*$. We do not observe $x^*$ directly; rather, we observe a noisy version $x$ of $x^*$ that itself is a GLM of $x^*$. The goal of the analysis is to estimate the effect of $x^*$ on $y$ using the observed data $(x , y)$ only. In the context of the biological application, $x^*$, $y$, and $x$ are CRISPR perturbations, gene expressions, and barcode counts, respectively.

Within this framework we make two contributions. First, we study the thresholding method from theoretical and empirical perspectives. We characterize the properties of the estimator and uncover settings in which

% Next, we propose a new method

GLM-EIV (GLM-based errors in variables). GLM-EIV implicitly estimates the probability that each cell was perturbed, thereby obviating the need to explicitly impute perturbation identities via thresholding or some other heuristic.

% Overall, we show how coupling novel, principled statistical approaches to current, powerful technologies from genomics and computer science -- namely, CRISPR genome engineering, single-cell sequencing, cloud computing, and high-performance computing -- can drive new biological insights.

@@

\section{Related work}
